Exploratory Plots

### 2020-06-10 exploratory/2020/README.Rmd
Add subheadings

```{r fit_db_sensspec}
sensspec <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.tsv')) %>%
  relevel_method()
sensspec %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = mcc, color = dataset)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  #ylim(0, 1) +
  facet_grid(dataset ~ ref)
```

```{r fit_db_benchmarks, warning=FALSE}
benchmarks <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.tsv')) %>%
  relevel_method
benchmarks %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = s, color = dataset)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Dark2") +
  #scale_color_manual(values = dataset_colors) +  # bug in geom_boxplot with manual colors?
  facet_wrap("ref") +
  labs(y = 'seconds')
```

```{r fit_db_ref_size}
ref_sizes <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/ref_sizes.tsv'))
kable(ref_sizes)
```

Potential problem: started with 174k reference sequences in RDP; filter with the hard parameter leaves only ~6k sequences remaining.

@@

```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.tsv'))
fractions %>% 
  ggplot(aes(x=dataset, y=fraction_mapped, color=dataset)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref") +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit")
```

>>>>

### Performance as measured by MCC
```{r fit_db_sensspec}
sensspec <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.tsv')) %>%
  relevel_method()
sensspec %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = mcc, color = dataset)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  #ylim(0, 1) +
  facet_grid(dataset ~ ref)
```

### Performance as measured by runtime
```{r fit_db_benchmarks, warning=FALSE}
benchmarks <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.tsv')) %>%
  relevel_method
benchmarks %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = s, color = dataset)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Dark2") +
  #scale_color_manual(values = dataset_colors) +  # bug in geom_boxplot with manual colors?
  facet_wrap("ref") +
  labs(y = 'seconds')
```

### Reference & dataset sizes
```{r fit_db_ref_size}
ref_sizes <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/ref_sizes.tsv'))
kable(ref_sizes)
```

@@

### Fraction of sequences that map to the reference
```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.tsv'))
fractions %>% 
  ggplot(aes(x=dataset, y=fraction_mapped, color=dataset)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref") +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit")
```
